Characterization of an anionic membrane mimetic with natural phospholipid content and magnetic orienting capabilities

### 2020-08-26 article.tex
5 revisiones enmendadas

	\renewcommand{\thefootnote}{\alph{footnote}}
	\section{Introduction}
	The cell is a highly complex unit present in all living organisms: it
	constitutes the building block of life. Essentially, consists in a closed
	domain
	containing smaller organelles in a highly complex and crowded aqueous solution,
	all enclosed by a bilayer made of mainly phospholipids and containing fatty
	acids, sugars, cholesterol and proteins, among others. This bilayer is called
	cell membrane or cytoplasmic membrane. Membranes itself are very complex
	molecular organizations with variable and inhomogeneous composition, and its
	atomic level understanding is a very difficult task. For this reason, the
	employment of
	membrane mimetics and models has become common practice.\cite{Bondar2019}\\
	Because of their ability to orient spontaneously when exposed to an external
	magnetic field, bilayered micelles, also called ``bicelles'', have been widely
	used as membrane mimetics, as they allow the use of solution NMR to probe the
	orientation and dynamics of liposomes and
	drugs\cite{Beaugrand2016,Montecinos2007,Ruiz-Fernandez2016}. Although a
	composition capable of forming magnetic orienting bicelles was described in the
	late 1960s\cite{Lawson1967}, the authors did not recognize the bicelle structure
	at the time, instead, ten years later Amaral \textit{et al.} were the first to
	identify the bicelle structure
	with a mixture of sodium decyl sulphate and
	1-decanol\cite{Amaral1979}. Later,
	in the 1990s, it was discovered that a
	mixture of DMPC\footnote{1,2-dimyristoyl-\textit{sn}-glycero-3-phosphocholine}
	and
	CHAPSO\footnote{3-(cholamidopropyl)dymethylammonio-2-hydroxy-1-propanesulfonate}
	forms magnetically orientable bicelles\cite{Sanders1990}, these aggregates are
	suitable to use as a membrane mimetics, as they contain
	phospholipid in their composition. Many improvements have been made to this
	composition over the years. It was found that CHAPSO can be replaced by
	DHPC\footnote{1,2-dihexanoyl-\textit{sn}-glycero-3-phosphocholine} which has a
	structure that resembles more to a natural phospholipid\cite{Sanders1992}, it
	was also found
	that the addition of cholesterol improves the stability of the
	bilayer\cite{Shapiro2010} and
	the addition of Triton X-100 detergent improves its magnetic orienting
	capabilities\cite{Park2010}. Nowadays, bicelles are considered good membrane
	mimetics, as they have been successfully employed to predict drug permeability
	through the membrane\cite{Sun2008,Durr2013,Matsumori2007,Koenig2005}, and to
	elucidate
	protein structures in the trans-membrane domain\cite{Durr2012}. The use of
	bicelles is ideal when
	the
	drug-detergent (or protein-detergent) complex is small (<\SI{100}{kDa}), as
	these systems can be studied in solution
	NMR\cite{Warschawski2011,Raschle2010,Sanders2006}. However, it should be
	pointed out that a single phospholipid bilayer by no means represents the
	complexity of the mixture found in natural membranes.\\

@@

	%channel\cite{Oakes2019,Martin2014,Shibata2005,Griepernau2007,EmmaTerama2008,DePaula2008,Cantor1998,Bernardi2009,Godwin2005}.
	% Despite which mechanisms are actually taking place, crossing membrane
	%interfaces
	% to become incorporated into the hydrophobic domain appears to be a crucial
	%step
	% for
	% most drugs.\\
	Benzocaine is a well-known local anesthetic for topical use. It has been widely
	employed anesthetizing the oropharynx for trans-esophageal echocardiography,
	bonchoscopy, esophagogastroduodenoscopy, in cold sores, mouth ulcers,
	toothache,
	sore gums and denture ache among others\cite{McEvoy2007}.
	% A significant number of
	% cases of Benzocaine induced cyanosis (methemoglobinemia) have been reported
	% along the
	% years\cite{Lardieri2019}, however it still remains in use.\\
	Benzocaine has been subject of a significant number of studies, including free
	energy transfer from water to the interior of different membrane
	mimetics\cite{Martin2014a,Cascales2011,Porasso2009,J.J.LopezCascales2006},
	estimations about location and orientation in different bilayers and
	monolayers\cite{Matsuki2001,Suwalsky2004,Kuroda2000,Choi2001}, interactions
	with
	a variety of
	solvents\cite{Cardenas2016,Cardenas2018,Paluch2015,Avila2002,Aguado2013} and
	encapsulation in different structures for controlled delivery
	purposes\cite{Shkurenko2018,AttouiYahia2017,Li2016,Arantes2014,Puglia2011}
	among
	others. All the evidence confirms that Benzocaine is able to cross the
	interface
	of membrane mimetics to become incorporated into the
	hydrophobic bilayer to finally be located at the inner interface.\\
	Contrary to most local anesthetics, Levodopa (or L-DOPA), the precursor of the
	neurotransmitter dopamine, commonly used in treatment of Parkinson's
	disease\cite{Fabbrini1987},
	is
	able to cross membrane interfaces only via active
	processes\cite{BENTLEY2012349,PRYOR2013180}.
	Therefore, in the absence of appropriate specific receptors, Levodopa should
	remain attached to the outer interface and should not reach the hydrophobic
	bilayer core\cite{Orowski2012}.\\

	In this article, we present a new anionic nematic lyotropic liquid crystal,
	with bilayer structure, susceptible to be used as membrane mimetic. It is made
	of sodium dodecyl sulfate (SDS), 1-decanol (DeOH), sodium sulphate
	(\ce{Na2SO4})
	and a mixture of natural phospholipids extracted from soybean, all dissolved in
	water. The structure of the mesophase, which spontaneously orients in magnetic
	fields,
	was characterized using polarized light microscopy textures and to observe the
	dynamics
	of the interface as well as deeper into the hydrophobic core, $^2$H-NMR
	quadrupole splittings from HDO, DeOH-$\alpha$-d$_2$, and SDS-d$_{25}$ were
	measured. To test the capability of the new mimetic to reproduce
	cell membrane behavior, Benzocaine and Levodopa were dissolved in the mesophase
	solution. According to previous evidence, Benzocaine should spontaneously be
	incorporated inside the bilayer and become located around the inner
	interface\cite{Martin2014a},
	whereas Levodopa should remain attached to the outer
	interface\cite{Orowski2012}. 
	To obtain an atomic detailed characterization of the mimetic dynamics and
	structure, including information about location, interface crossing dynamics
	and
	interactions of Benzocaine and Levodopa with the bilayer components, the
	spectroscopic measurements were complemented with classical molecular dynamics
	(MD) simulations.

@@

	In order to achieve a membrane mimetic that behaves as similar as possible to
	the actual cellular membrane, it is necessary to maximize its phospholipid
	concentration. This is important considering that multiple researchers have
	concluded that there are specific interactions between phosphate from the
	multiple phospholipids and certain amino-acids that modify the membrane
	permeability where this interaction occurs\cite{Aliaga2011,Hristova2011}.\\
	Also, the membrane mimetic must orient itself in presence of an external
	magnetic field. This is so the deuterated probes in the mimetic can produce a
	\textit{quadrupole splitting} in a solution $^2$H-RMN spectrum, which will be
	used to calibrate the MD simulations. This calibrated simulation can be used to
	assess other properties, not possible to measure experimentally, with more
	confidence.\\

@@

	Polarized light microscopy of the mesophase shows a thread-like pattern, this
	is
	characteristic of a lyotropic nematic phase\cite{dierking2006textures}.
	Furthermore, considering the magnitude of the measured quadrupolar
	splittings, and the fact that each methylene's deuteron pair in SDS-d$_{25}$
	yields
	a
	single quadrupolar splitting in solution $^2$H-NMR (see figure
	\ref{fig:reference}), we can conclude that this phase has a bilayer
	like structure with its bilayer normal perpendicular
	to the magnetic field ($\theta=\pi/2$ in eq. \ref{eq:splitting}). The
	posibility of a calamitic phase is discarded, since a calamitic phase implies a
	director axis being parallel to the magnetic field ($\theta=0$ in eq.
	\ref{eq:splitting}) which would produce splittings considerably smaller than
	observed.\\

@@

	A $^2$H-NMR spectrum from a membrane mimetic sample with \SI{8}{mg}
	Benzocaine added per gram of mimetic enriched with SDS-d$_{25}$ was obtained
	and compared
	with the spectrum of the same mimetic without the anesthetic (Differences
	displayed in figure
	\ref{fig:sds_benzocaine}). It can be seen that the presence
	of
	Benzocaine alters the quadrupolar splittings of the SDS aliphatic chain 
	from the first up to the sixth carbon, implying that Benzocaine is mostly
	residing in this zone, perturbing the order of these methylenes.
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth]{sds_variation}
		\caption{Variation on quadrupolar splittings in $^2$H-NMR upon adding
			Benzocaine or Levodopa to a membrane mimetic sample enriched with
			SDS-d$_{25}$.}
		\label{fig:sds_benzocaine}
	\end{figure}
	Employing the calibrated model stated before, a potential of mean force (PMF)
	profile for the process of Benzocaine permeating the membrane mimetic along a
	path perpenticular to the interface, was calculated
	(figure \ref{fig:benzocaine_profile}). From this PMF profile it can be deduced
	that
	in order to complete its
	translocation, Benzocaine goes through three steps:
	First, it integrates spontaneously with the outer leaflet of the bilayer,
	without mayor interactions with the Stern layer, judged by the lack of an
	energy barrier in this area. Secondly, Benzocaine
	``flip-flops'' to the opposite leaflet of the bilayer with a small activation
	energy (\SI{11.2}{\kilo\joule}). And third and finally, it escapes the bilayer
	into the bulk at a minor energetic cost (\SI{27.1}{kJ}), showing that
	Benzocaine
	permeation through the membrane mimetic is indeed possible.\\
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth]{benzo_profile_density}
		\caption{Mean force potential profile for the process of Benzocaine
			translocating through a membrane mimetic. The blue dotted area represents
			the water particle density, while the smooth orange area represents the
			lipid particle density in the simulation.}
		\label{fig:benzocaine_profile}
	\end{figure}
	This mechanism is in agreement with the spectroscopic results
	(displayed in figure \ref{fig:sds_benzocaine}), in both cases, the most
	probable
	position for Benzocaine to be in, is indeed inside the bilayer and close to the
	inner
	interface.\\

@@

	\section{Conclusions}
	Multiple researchers\cite{Aliaga2011,Hristova2011} have found
	that there is a specific interaction between arginine and the phosphate group
	from
	phospholipids
	that modify the properties of the membrane where this interaction occurs.
	Therefore, the inclusion of an important amount of a natural phospholipid
	mixture makes this nematic lyotropic liquid crystal able to allow such
	interactions to occur, making this mimetic a closer representation of a real
	cellular membrane.\\
	Additionally, the low cost of this mimetic components, compared to the classic
	bicelles, makes it feasible to perform drugs and peptides permeability studies
	more massively.\\
	Also, the ability of the mesophase to orient itself in an external magnetic
	field
	makes this membrane mimetic useful for studies of structure and dynamics
	employing solution
	$^2$H-NMR.\\
	In addition, we have developed a MD model calibrated to reproduce
	experimentally measured mesophase order paramteres. Using this developed model,
	PMF profiles of Benzocaine and Levodopa crossing the bilayer interface were
	calculated, and the results reproduce the experimental observations, allowing to
	obtain information about the translocating process that is	unfeasible to obtain
	via experimental means.\\
	Finally, having proven that Benzocaine, a local anesthetic that permeates
	the cellular membrane, is able to translocate through the developed membrane
	mimetic; and that Levodopa, an amino-acid that cannot passively permeate the
	cellular membrane, is unable to do so through the membrane
	mimetic, we conclude that the developed membrane mimetic has
	similar permeation properties as a cellular membrane, and thus, validating this
	mesophase as an actual
	membrane mimetic.\\

>>>>

	\renewcommand{\thefootnote}{\alph{footnote}}
	\section{Introduction}
	The cell is a highly complex unit present in all living organisms: it
	constitutes the building block of life. Essentially, consists in a closed
	domain
	containing smaller organelles in a highly complex and crowded aqueous solution,
	all enclosed by a bilayer made of mainly phospholipids among other lipids and
  also containing sugars, cholesterol and proteins, among others. This bilayer is called
	cell membrane or cytoplasmic membrane. Membranes itself are very complex
	molecular organizations with variable and inhomogeneous composition, and its
	atomic level understanding is a very difficult task. For this reason, the
	employment of
	membrane mimetics and models has become common practice.\cite{Bondar2019}\\
	Because of their ability to orient spontaneously when exposed to an external
	magnetic field, bilayered micelles, also called ``bicelles'', have been widely
	used as membrane mimetics, as they allow the use of solution NMR to probe the
	orientation and dynamics of liposomes and
	drugs\cite{Beaugrand2016,Montecinos2007,Ruiz-Fernandez2016}. Although a
	composition capable of forming magnetic orienting bicelles was described in the
	late 1960s\cite{Lawson1967}, the authors did not recognize the bicelle structure
	at the time, instead, ten years later Amaral \textit{et al.} were the first to
	identify the bicelle structure
	with a mixture of sodium decyl sulphate and
	1-decanol\cite{Amaral1979}. Later,
	in the 1990s, it was discovered that a
	mixture of DMPC\footnote{1,2-dimyristoyl-\textit{sn}-glycero-3-phosphocholine}
	and
	CHAPSO\footnote{3-(cholamidopropyl)dymethylammonio-2-hydroxy-1-propanesulfonate}
	forms magnetically orientable bicelles\cite{Sanders1990}, these aggregates are
	suitable to use as a membrane mimetics, as they contain
	phospholipid in their composition. Many improvements have been made to this
	composition over the years. It was found that CHAPSO can be replaced by
	DHPC\footnote{1,2-dihexanoyl-\textit{sn}-glycero-3-phosphocholine} which has a
	structure that resembles more to a natural phospholipid\cite{Sanders1992}, it
	was also found
	that the addition of cholesterol improves the stability of the
	bilayer\cite{Shapiro2010} and
	the addition of Triton X-100 detergent improves its magnetic orienting
	capabilities\cite{Park2010}. Nowadays, bicelles are considered good membrane
	mimetics, as they have been successfully employed to predict drug permeability
	through the membrane\cite{Sun2008,Durr2013,Matsumori2007,Koenig2005}, and to
	elucidate
	protein structures in the trans-membrane domain\cite{Durr2012}. The use of
	bicelles is ideal when
	the
	drug-detergent (or protein-detergent) complex is small (<\SI{100}{kDa}), as
	these systems can be studied in solution
	NMR\cite{Warschawski2011,Raschle2010,Sanders2006}. However, it should be
	pointed out that a single phospholipid bilayer by no means represents the
	complexity of the mixture found in natural membranes.\\

@@

	%channel\cite{Oakes2019,Martin2014,Shibata2005,Griepernau2007,EmmaTerama2008,DePaula2008,Cantor1998,Bernardi2009,Godwin2005}.
	% Despite which mechanisms are actually taking place, crossing membrane
	%interfaces
	% to become incorporated into the hydrophobic domain appears to be a crucial
	%step
	% for
	% most drugs.\\
	Benzocaine is a well-known local anesthetic for topical use. It has been widely
	employed anesthetizing the oropharynx for trans-esophageal echocardiography,
	bonchoscopy, esophagogastroduodenoscopy, in cold sores, mouth ulcers,
	toothache,
	sore gums and denture ache among others\cite{McEvoy2007}.
	% A significant number of
	% cases of Benzocaine induced cyanosis (methemoglobinemia) have been reported
	% along the
	% years\cite{Lardieri2019}, however it still remains in use.\\
	Benzocaine has been subject of a significant number of studies, including free
	energy transfer from water to the interior of different membrane
	mimetics\cite{Martin2014a,Cascales2011,Porasso2009,J.J.LopezCascales2006},
	estimations about location and orientation in different bilayers and
	monolayers\cite{Matsuki2001,Suwalsky2004,Kuroda2000,Choi2001}, interactions
	with
	a variety of
	solvents\cite{Cardenas2016,Cardenas2018,Paluch2015,Avila2002,Aguado2013} and
	encapsulation in different structures for controlled delivery
	purposes\cite{Shkurenko2018,AttouiYahia2017,Li2016,Arantes2014,Puglia2011}
	among
	others. All the evidence confirms that Benzocaine is able to cross the
	interface
	of membrane mimetics to become incorporated into the
	hydrophobic bilayer to finally be located along the first carbons of the
  aliphatic chains, remaining close to the interface at equilibrium. \\
	Contrary to most local anesthetics, Levodopa (or L-DOPA), the precursor of the
	neurotransmitter dopamine, commonly used in treatment of Parkinson's
	disease\cite{Fabbrini1987},
	is
	able to cross membrane interfaces only via active
	processes\cite{BENTLEY2012349,PRYOR2013180}.
	Therefore, in the absence of appropriate specific receptors, Levodopa should
	remain attached to the outer interface and should not reach the hydrophobic
	bilayer core\cite{Orowski2012}.\\

	In this article, we present a new anionic nematic lyotropic liquid crystal,
	with bilayer structure, susceptible to be used as membrane mimetic. It is made
	of sodium dodecyl sulfate (SDS), 1-decanol (DeOH), sodium sulphate
	(\ce{Na2SO4})
	and a mixture of natural phospholipids extracted from soybean, all dissolved in
	water. The structure of the mesophase, which spontaneously orients in magnetic
	fields,
	was characterized using polarized light microscopy textures and to observe the
	dynamics
	of the interface as well as deeper into the hydrophobic core, $^2$H-NMR
	quadrupole splittings from HDO, DeOH-$\alpha$-d$_2$, and SDS-d$_{25}$ were
	measured. To test the capability of the new mimetic to reproduce
	cell membrane behavior, Benzocaine and Levodopa were dissolved in the mesophase
	solution. According to previous evidence, Benzocaine should spontaneously be
	incorporated inside the bilayer and become located around the first carbons of
  the aliphatic chains\cite{Martin2014a},
	whereas Levodopa should remain along the Stern layer of the interface without
  entering the bilayer\cite{Orowski2012}. 
	To obtain an atomic detailed characterization of the mimetic dynamics and
	structure, including information about location, interface crossing dynamics
	and
	interactions of Benzocaine and Levodopa with the bilayer components, the
	spectroscopic measurements were complemented with classical molecular dynamics
	(MD) simulations.

@@

	In order to achieve a membrane mimetic that behaves as similar as possible to
  the actual cellular membrane, it is necessary to maximize its phospholipid
  concentration. The presence of phospholipids in a membrane mimetic is
  specially important, not only because they are a major structural element in
  biological membranes, but also because their zwitterionic (or anionic)
  characteristic grants additional stability to the lamellar phase.
  Additionally, multiple researchers have concluded that there are
  specific interactions between phosphate from the multiple phospholipids and
  certain amino-acids that modify the membrane
	permeability where this interaction occurs\cite{Aliaga2011,Hristova2011}.\\

	Another condition that the mimetic must fulfill, is that the mimetic must
  orient itself in presence of an external magnetic field. This is so the
  deuterated probes in the mimetic can produce a \textit{quadrupole splitting}
  in a solution $^2$H-RMN spectrum, which will be used to calibrate the MD
  simulations. This calibrated simulation can be used to assess other
  properties, not possible to measure experimentally, with more
	confidence.\\

@@

	Polarized light microscopy of the mesophase shows a thread-like pattern, this
	is
	characteristic of a lyotropic nematic phase\cite{dierking2006textures}.
	Furthermore, considering the magnitude of the measured quadrupolar
	splittings, and the fact that each methylene's deuteron pair in SDS-d$_{25}$
	yields
	a
	single quadrupolar splitting in solution $^2$H-NMR (see figure
	\ref{fig:reference}), we can conclude that this phase has a bilayer
	like structure with its bilayer normal perpendicular
	to the magnetic field ($\theta=\pi/2$ in eq. \ref{eq:splitting}). The
	posibility of a calamitic phase is discarded, since a calamitic phase implies a
	director axis being parallel to the magnetic field ($\theta=0$ in eq.
	\ref{eq:splitting}) which would produce splittings considerably smaller than
	observed. Regarding the size of the aggregate, cryo-TEM imagery of similar
  bicelles (made with TTA\footnote{Trimethyltetradecylammonium} instead of SDS)
  results in aggregates of about
  \SI{2}{nm}-\SI{5}{nm}\todo{RSCAdv.,2016,6,7455}, and we expect for the size of
  the membrane mimetic aggregate to be in the same order of magnitude.\\

@@

	A $^2$H-NMR spectrum from a membrane mimetic sample with \SI{8}{mg}
	Benzocaine added per gram of mimetic enriched with SDS-d$_{25}$ was obtained
	and compared
	with the spectrum of the same mimetic without the anesthetic (Differences
	displayed in figure
	\ref{fig:sds_benzocaine}). It can be seen that the presence
	of
	Benzocaine alters the quadrupolar splittings of the SDS aliphatic chain 
	from the first up to the sixth carbon, implying that Benzocaine is mostly
	residing in this zone, perturbing the order of these methylenes.
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth]{sds_variation}
		\caption{Variation on quadrupolar splittings in $^2$H-NMR upon adding
			Benzocaine or Levodopa to a membrane mimetic sample enriched with
			SDS-d$_{25}$.}
		\label{fig:sds_benzocaine}
	\end{figure}
	Employing the calibrated model stated before, a potential of mean force (PMF)
	profile for the process of Benzocaine permeating the membrane mimetic along a
	path perpenticular to the interface, was calculated
	(figure \ref{fig:benzocaine_profile}). From this PMF profile it can be deduced
	that
	in order to complete its
	translocation, Benzocaine goes through three steps:
	First, it integrates spontaneously with the outer leaflet of the bilayer,
	without mayor interactions with the Stern layer, judged by the lack of an
	energy barrier in this area. Secondly, Benzocaine
	``flip-flops'' to the opposite leaflet of the bilayer with a small activation
	energy (\SI{11.2}{\kilo\joule}). And third and finally, it escapes the bilayer
	into the bulk at a minor energetic cost (\SI{27.1}{kJ}), showing that
	Benzocaine
	permeation through the membrane mimetic is indeed possible.\\
	\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth]{benzo_profile_density}
		\caption{Mean force potential profile for the process of Benzocaine
			translocating through a membrane mimetic. The blue dotted area represents
			the water particle density, while the smooth orange area represents the
			lipid particle density in the simulation.}
		\label{fig:benzocaine_profile}
	\end{figure}
	This mechanism is in agreement with the spectroscopic results
	(displayed in figure \ref{fig:sds_benzocaine}), in both cases, the most
	probable
	position for Benzocaine to be in, is indeed inside the bilayer and close to the
	interface.\\

@@

	\section{Conclusions}
	Multiple researchers\cite{Aliaga2011,Hristova2011} have found
	that there is a specific interaction between arginine and the phosphate group
	from
	phospholipids
	that modify the properties of the membrane where this interaction occurs.
	Therefore, the inclusion of an important amount of a natural phospholipid
	mixture makes this nematic lyotropic liquid crystal able to allow such
	interactions to occur. This, added to the additional stability that the
  presence of phospholipids grants, makes this mimetic a closer representation of a real
	cellular membrane.\\
	Additionally, the low cost of this mimetic components, compared to the classic
	bicelles, makes it feasible to perform drugs and peptides permeability studies
	more massively.\\
	Also, the ability of the mesophase to orient itself in an external magnetic
	field
	makes this membrane mimetic useful for studies of structure and dynamics
	employing solution
	$^2$H-NMR.\\
	In addition, we have developed a MD model calibrated to reproduce
	experimentally measured mesophase order paramteres. Using this developed model,
	PMF profiles of Benzocaine and Levodopa crossing the bilayer interface were
	calculated, and the results reproduce the experimental observations, allowing to
	obtain information about the translocating process that is	unfeasible to obtain
	via experimental means.\\
	Finally, having proven that Benzocaine, a local anesthetic that permeates
	the cellular membrane, is able to translocate through the developed membrane
	mimetic; and that Levodopa, an amino-acid that cannot passively permeate the
	cellular membrane, is unable to do so through the membrane
	mimetic, we conclude that the developed membrane mimetic has
	similar permeation properties as a cellular membrane, and thus, validating this
	mesophase as an actual
	membrane mimetic.\\

### 2020-08-26 revision_cover_letter.tex
5 revisiones enmendadas

>>>>

  Regarding the observations both of the reviewers, we have made multiple changes to
  our manuscript in order to amend the issues found by the reviewers, as
  follows:

  \begin{itemize}
  \item Reviewer 1 said: \textit{...}\\
    We Agree, fatty acids are not present by themselves in the membrane, but
    rather as a fragment of bigger lipids such as glycolipids, shpingolipids and
    phospholipids among others. And thus, we have changed the phrasing from
    \textit{``...mainly phospholipids and containing fatty acids, sugars,
      cholesterol and proteins, among others.''} to \textit{``mainly phospholipids among other lipids and
      also containing sugars, cholesterol and proteins, among others.''}

  \item Reviewer 1 said: \textit{...}\\
    We have not made ourselves clear in this regard. When we wrote ``inner
    interface'' we meant the area inside the bilayer that is closer to the
    interface. And in that regard, the results by Martin \textit{et al.} show
    that Benzocaine is indeed located in this area at equilibrium. We modified
    all mentions of ``inner interface'' to reflect what we actually meant.

  \item Reviewer 1 said: \textit{tamaño de la bicela}\\

  \item Reviewer 1 said: \textit{...}}\\
  We agree, and we have modified such sections to include the role of
  phospholipids in the phase stability\

\item Reviewer 1 said: \textit{...}\\
  Agreed, and we have added the following sentence to fulfill the missing
  information: ``\textit{Regarding the size of the aggregate, cryo-TEM imagery of similar
  bicelles (made with TTA instead of SDS)
  results in aggregates of about
  \SI{2}{nm}-\SI{5}{nm}, and we expect for the size of
  the membrane mimetic aggregate to be in the same order of magnitude.}''
\item Reviewer 1 said: \textit{By the same reasoning, the orientation of
    bicelles reflect their size/anisotropy in the NMR time scale. It is not
    that ``it orient ifself'' as stated here: “Also, the membrane mimetic
    must orient itself in presence of an external magnetic field. This is so the
  deuterated probes in the mimetic can produce a quadrupole splitting in a
  solution 2H-RMN spectrum”. Please rephrase that.}

\item Reviewer 1 said: \textit{Item 3.4.1 Once more the authors states that
    benzocaine inserts the bilayer ang get ``close to the inner interface'' as if
    it was the internal monolayer (see question 2). I think they meant ``inside the
    bilayer, nearby the glycerol moiety / polar head group region''. }\\
  We agree, and as stated before, we have amended all mentions of the ``inner
  interface'' so there would be no misunderstantings.
\item Reviewer 1 said: \textit{Fig. 9, what is the reason for the change in
    frequency (-100 Hz to + 100 Hz) observed with levoDOPA, in the acyl chain
    carbons 4-5?}

 \end{itemize}

   Finally, we would like to thank you for taking your time to revise our
   manuscript, even through these difficult times.
